Generate data for multispecies modeling, including diet!

### 2020-09-14 NOBAmsdiets.Rmd
compare polygon/layer diet, check global

@@

# how many polygons included? how many layers per polygon have data?
cod5det %>% group_by(time.days, polygon, layer) %>% tally()

# are there differences by layer within a polygon?
#    polygons 12 and 19 are on the slope, have most layers with agecl 5 cod
cod5det1219 <- cod5det %>%
  filter(polygon %in% c(12,19))

@@

### Diets by polygon and layer {.tabset}

@@

```{r detdiet-vis2}
# are there differences by polygon? (aggregate layers)
cod5det_agg <- cod5det %>%
  group_by(species, agecl, time.days, polygon, prey) %>%
  summarise(polytons = sum(atoutput))

ggplot(cod5det_agg, aes(time.days/365, polytons, fill=prey)) + 
    geom_bar(stat = "identity") +
    facet_wrap(polygon) +
    xlab("year") +
    ylab("diet tons") +
    theme_tufte() +
    theme(legend.position="bottom")

@@

>>>>

```{r}
# read in the saved file
source(here("config", "NOBA2config.R"))

ms_detaileddiet <- readRDS(file.path(d.name, paste0(scenario.name, "ms_detaileddiet.rds")))

@@

# how many polygons included? how many layers per polygon have data?
#cod5det %>% group_by(time.days, polygon, layer) %>% tally()
# why are layers -1 and 0 included (must have trace data if 0 diet was eliminated)

# are there differences by layer within a polygon?
#    polygons 12 and 19 are on the slope, have most layers with agecl 5 cod
cod5det1219 <- cod5det %>%
  filter(polygon %in% c(1,6,7,12,19,25,29,37))

@@

As suspected, diet composition varies greatly by model area and layer.

### Consumption by polygon and layer {.tabset}

#### Cod agecl 5 polygon 1
```{r, fig.width=9, fig.height=9}
plist2$'1'
```

#### Cod agecl 5 polygon 6
```{r, fig.width=9, fig.height=9}
plist2$'6'
```

#### Cod agecl 5 polygon 7
```{r, fig.width=9, fig.height=9}
plist2$'7'
```

@@

#### Cod agecl 5 polygon 25
```{r, fig.width=9, fig.height=9}
plist2$'25'
```

#### Cod agecl 5 polygon 29
```{r, fig.width=9, fig.height=9}
plist2$'29'
```

#### Cod agecl 5 polygon 37
```{r, fig.width=9, fig.height=9}
plist2$'37'
```

```{r detdiet-poly}
# are there differences by polygon? (aggregate layers)
coddet_agg <- as.data.frame(
  ms_detaileddiet %>%
  filter(species=="North_atl_cod") %>%
  group_by(species, agecl, time.days, polygon, prey) %>%
  summarise(polytons = sum(atoutput))
)

coddet_agg2 <- atlantisom::aggregateData(dat = ms_detaileddiet, 
                                        time = unique(ms_detaileddiet$time.days), 
                                        species = "North_atl_cod", 
                                        boxes = unique(ms_detaileddiet$polygon),
  keepColumns = c("species", "agecl", "polygon", "time.days", "prey"))

names(coddet_agg2)[names(coddet_agg2)=="numAtAge"] <- "polytons"

plist3 = lapply(split(coddet_agg2, coddet_agg2$agecl), function(d) {
  ggplot(d, aes(time.days/365, polytons, fill=prey)) + 
    geom_bar(stat = "identity") +
    facet_wrap(species~polygon) +
    xlab("year") +
    ylab("diet tons") +
    theme_tufte() +
    theme(legend.position="bottom")
})

@@

#### Cod agecl 5 all polygons
```{r, fig.width=9, fig.height=9}
plist3$'5'
```

#### Cod agecl 10 all polygons
```{r, fig.width=9, fig.height=9}
plist3$'10'
```

Aggregate across layers and polygons, compare to aggreate diet comp output (proportion) and biomass_eaten estimate:

```{r detdiet-all, fig.width=9, fig.height=9}
# are there differences by polygon? (aggregate layers)
coddet_aggall <- as.data.frame(
  coddet_agg %>%
  filter(species=="North_atl_cod") %>%
  group_by(species, agecl, time.days, prey) %>%
  summarise(tottons = sum(polytons))
)

  ggplot(coddet_aggall, aes(time.days/365, tottons, fill=prey)) + 
    #geom_bar(stat = "identity") +
    geom_bar(position = "fill", stat = "identity") +
    facet_wrap(species~agecl) +
    xlab("year") +
    ylab("diet tons") +
    theme_tufte() +
    theme(legend.position="bottom")
```
